Analyzing Trends in Crime Against Persons: Insights from the Toronto Police Annual Statistical Report

### 2024-01-25 outputs/paper/paper.qmd
Final Draft

Concern of public safety in the urban societies is a necessary step towards safeguarding the residents of that community. The city of Toronto has various socio-economic challenges one of them being crime against a person. A crime incident might leave a victim and our report aims to explore the patterns and trend of crimes against the person. The paper aims to understand how this trends have evolved among victims and to analyze their demographics from 2014 to 2022. Furthermore, it's important to note that the report's scope extends beyond merely quantifying crime victims but it also interpret and explain whereby it motivates to a better approach towards urban safety and policies. The Criminal victimization is a frightening and unsettling experience for many Canadians (@statscanada).
Victimology is a vast sub-category of criminology to understand various emotional factors and its causation, however based on our police annual report – victims of  crime showcase a statistical record based on which the report will share the knowledge to work on the gap to understand between victim demographics and crime. This report addresses this gap by visualizing crime statistics through a demographic lens, thereby unveiling patterns that may not be evident in numerical data alone. Through R programming language [@R], in this report, we analyze the data obtained. from Open data Toronto Portal [@rOpenDataToronto]. This dataset provides a detailed account of all recorded count of victim under the jurisdiction of the Toronto Police Services over an eight-period. Our research offers an examination of cleaned data points and produced visual formats that reveal the shapes the crime type as well as their victims across different genders and age cohorts. The analysis, supplemented with various analytical tools like Tidyverse [@rTidyverse], AER [@rAER], Janitor [@rJanitor], and Knitr [@rKnitr], delves deep into the trends, revealing patterns that could have implications for policy formulation and implementation. The introduction is followed by the data section. Within the data section we talk about the data source used for this report, the data cleaning process applied and the result that is the visual analysis of trends and pattern involved. The Discussion section shares additional insights into the data findings, as well as discussing measurement errors and limitations of this analysis. Lastly, the document summarizes the analysis with conclusion.

>>>>

Concern of public safety in the urban societies is a necessary step towards safeguarding the residents of that community. The city of Toronto has various socio-economic challenges one of them being crime against a person. A crime incident might leave a victim and our report aims to explore the patterns and trend of crimes against the person. The paper aims to understand how this trends have evolved among victims and to analyze their demographics from 2014 to 2022. Furthermore, it's important to note that the report's scope extends beyond merely quantifying crime victims but it also interpret and explain whereby it motivates to a better approach towards urban safety and policies. The Criminal victimization is a frightening and unsettling experience for many Canadians (@statscanada).
Victimology is a vast sub-category of criminology to understand various emotional factors and its causation, however based on our police annual report – victims of  crime showcase a statistical record based on which the report will share the knowledge to work on the gap to understand between victim demographics and crime. This report addresses this gap by visualizing crime statistics through a demographic lens, thereby unveiling patterns that may not be evident in numerical data alone. Through R programming language [@R], in this report, we analyze the data obtained. from Open data Toronto Portal [@rOpenDataToronto]. This dataset provides a detailed account of all recorded count of victim under the jurisdiction of the Toronto Police Services over an eight-period. Our research offers an examination of cleaned data points and produced visual formats that reveal the shapes the crime type as well as their victims across different genders and age cohorts. The analysis, supplemented with various analytical tools like Tidyverse [@rTidyverse], AER [@rAER], Janitor [@rJanitor], and Knitr [@rKnitr], delves deep into the trends, revealing patterns that could have implications for policy formulation and implementation. Following this introduction, the Data section discusses our data sources, cleaning process, and the resultant visual analysis. The Discussion section delves into the implications of our findings, addressing potential measurement errors and limitations. Finally, the paper concludes with a summary of our analysis and its implications for policy formulation
